An Efficient Forecasting Approach\\ to Reduce Boundary Effects in Real-Time Time-Frequency Analysis

### 2020-08-27 Notes/results.tex
new figs

\paragraph{Influence of the Noise Variance $\sigma^2$} Here, the size of the training dataset is set to $K=450$. Then, the forecasting algorithm is run on $1000$ realizations on the discrete signal $\bx$ for three different values of $\sigma$, logarithmically equispaced from $10^{-3}$ to $10^{-1}$. For each of these values, we determine the experimental bias, denoted as $\mu_{\xp}[N-1+\ell]$, and experimental variance, denoted as $\gamma_{\xp}[N-1+\ell,N-1+\ell]$, in function of the forecasting sample index $\ell$ (going from $1$ to $L=100$).

The experimental results show that the bias is neither depending on the noise variance $\sigma^2$ nor the forecasting length $\ell$. Indeed, independently of $\sigma$, we always have $\mu_{\xp}[N-1+\ell]\in\left[-0.03\sigma,0.03\sigma\right]$, which is negligible with respect to the magnitude of $\bz$. This result does not contradict the theoretical result~\eqref{eq:mean.error} of Theorem~\ref{th:error} insofar as the bound is not reached. In Fig.~\ref{fig:res.noise.sine}, we display the experimental variance $\gamma_{\xp}[N-1+\ell,N-1+\ell]$ for each value of $\sigma$. The associated theoretical asymptotic forecasting variance~\eqref{eq:cov.error.2} is also displayed in solid line. As expected, this result highlights the fact that the forecasting variance increases linearly with respect to $\sigma^2$. The {\em slight} decrease of the forecasting variance with $\ell$ is characteristic of the stationarity of the forecast signal. This shows that as $\ell$ increases, the prediction becomes less correlated with the measurement noise.

\begin{figure}
\centering
%\includegraphics[width=.24\textwidth]{biasNoiseSine.eps}
\includegraphics[width=.48\textwidth]{VarianceNoiseSine.eps}
\caption{Evolution of the experimental and theoretical forecasting variance in function of the forecasting sample index for different values of $\sigma$.}
\label{fig:res.noise.sine}
\end{figure}

\paragraph{Influence of the Training Dataset Size $K$} Here, the noise variance $\sigma$ is set to $\sigma=10^{-2}$. Then, {\sf SigExt} is run on 3000 realizations of the discrete signal $\bx$ for three different values of $K$, logarithmically equispaced from $4.5\times 10^{2}$ to $2\times 10^{3}$. For each of these values, we determine the experimental bias $\mu_{\xp}[N-1+\ell]$ and variance $\gamma_{\xp}[N-1+\ell,N-1+\ell]$ in function of the forecasting sample index $\ell$, going from $1$ to $500$.

As in the previous study, the experimental bias becomes negligible when $K$ increases, confirming the approximation result~\eqref{eq:mean.error}. Besides, the experimental variance  is displayed in Fig.~\ref{fig:res.size.sine}, and compared with the associated theoretical variance~\eqref{eq:cov.error.2}. Each color corresponds to these experimental results obtained for a given value of $K$. This result validates the asymptotic behavior provided by~\eqref{eq:cov.error.2}, and we can show that the second-order moment $\gamma[\ell,\ell]$ is less dependent on $K$ when $K$ is large.

\begin{figure}
%\includegraphics[width=.24\textwidth]{BiasKSine.eps}
\includegraphics[width=.48\textwidth]{VarianceKSine.eps}
\caption{Evolution of the experimental and theoretical forecasting variance in function of the forecasting sample index for different values of $K$.}
\label{fig:res.size.sine}
\end{figure}

\paragraph{Summary}
Both previous experimental results combined with the theoretical asymptotic equation~\eqref{eq:cov.error.2} allow us to describe the influence of the noise variance and the size of the training dataset on the variance of the forecasting noise, empirically summarized as follows:
\begin{equation}
\gamma[N-1+\ell,N-1+\ell] \underset{K\to\infty}{\approx} \dfrac{\sigma^2}{K}g[\ell] .
\end{equation} 
where $g$ is a bounded positive function. The empirical result is coherent with the theoretical result provided by Theorem~\ref{th:error}.

This study neglects the analysis of the influence of the parameter $M$, whose influence on the value of the experimental variance is numerically not significant as long as $M\ll 2K$. The choice of this parameter is especially crucial when the deterministic component of the signal is no longer stationary. The AHM, discussed below, is an example.

>>>>

\paragraph{Influence of the Noise Variance $\sigma^2$} Here, the size of the training dataset is set to $K=450$. Then, the forecasting algorithm is run on $500$ realizations on the discrete signal $\bx$ for $200$ different values of $\sigma$, logarithmically equispaced from $10^{-7}$ to $10^{-1}$. For each of these values, we determine the experimental bias, denoted as $\mu_{\xp}[N-1+\ell]$, and experimental variance, denoted as $\gamma_{\xp}[N-1+\ell,N-1+\ell]$. Fig.~\ref{fig:res.noise.sine} shows the the experimental forecasting variance in function of the noise standard deviation for three different values the forecasting sample index: $\ell=1$, $\ell=10$, and $\ell=100$.

\begin{figure}
\centering
%\includegraphics[width=.24\textwidth]{biasNoiseSine.eps}
\includegraphics[width=.48\textwidth]{VarianceNoiseSine.eps}
\caption{Evolution of the experimental forecasting variance in function of the noise standard deviation for three different values the forecasting sample index $\ell$.}
\label{fig:res.noise.sine}
\end{figure}

{\color{blue}
Comment Fig. + Comparison with Theorem 1
}

\paragraph{Influence of the Training Dataset Size $K$} Here, the noise variance $\sigma$ is set to $\sigma=10^{-2}$. Then, {\sf SigExt} is run on $500$ realizations of the discrete signal $\bx$ for $200$ different values of training dataset size $K$, logarithmically equispaced from $450$ to $2000$. For each of these values, we determine the experimental bias $\mu_{\xp}[N-1+\ell]$ and variance $\gamma_{\xp}[N-1+\ell,N-1+\ell]$. Fig.~\ref{fig:res.size.sine} shows the the experimental forecasting variance in function of the training dataset size for three different values the forecasting sample index: $\ell=1$, $\ell=10$, and $\ell=100$.

\begin{figure}
%\includegraphics[width=.24\textwidth]{BiasKSine.eps}
\includegraphics[width=.48\textwidth]{VarianceKSine.eps}
\caption{Evolution of the experimental forecasting variance in function of the dataset size for three different values the forecasting sample index $\ell$.}
\label{fig:res.size.sine}
\end{figure}

{\color{blue}
{\color{blue}
Comment Fig. + Comparison with Theorem 1
}

%\paragraph{Summary}
%Both previous experimental results combined with the theoretical asymptotic equation~\eqref{eq:cov.error.2} allow us to describe the influence of the noise variance and the size of the training dataset on the variance of the forecasting noise, empirically summarized as follows:
%\begin{equation}
%\gamma[N-1+\ell,N-1+\ell] \underset{K\to\infty}{\approx} \dfrac{\sigma^2}{K}g[\ell] .
%\end{equation} 
%where $g$ is a bounded positive function. The empirical result is coherent with the theoretical result provided by Theorem~\ref{th:error}.
}

This study neglects the analysis of the influence of the parameter $M$, whose influence on the value of the experimental variance is numerically not significant as long as $M\ll 2K$ and $\ell<M$. The choice of this parameter is especially crucial when the deterministic component of the signal is no longer stationary. The AHM, discussed below, is an example.
